### 2015-06-29 narrative/intro.tex
More polishing

To address these challenges we will We are proposing to combine knowledge
from a wide range of sources including ORNL applications, the ADIOS project,
the SNL Lightweight File Systems project and storage system knowledge, the metadata
management and storage systems knowledge of UCSC, and the middleware expertise
of Rutgers. We will integrate this diverse expertise to investigate how to make
a data, workflow, and application aware storage system.

@@

In this project we will extend ADIOS~\cite{adios} with new APIs and novel techniques
to coordinate with the storage back-end. The key idea is offering the ability to
negotiate with the storage system to agree on the tradeoff between data quality
and response time. We will test our ideas on the next generation OLCF,
SNL/LANL, and NERSC systems.
%
In this project we will make use of the many inovations we discovered in 
the Lightweight File Systems~\cite{lwfs} (LWFS) project, where Sandia sought to
demonstrate stripping down a file system to the bare minimum features required
for any storage system. Then, additional functionality and semantics, such as
POSIX-style directories and consistency requirements, are added in using
auxiliary services separate from the stack or by layering providing a new
interface to the storage system. The project's first phase demonstrated that
using a core object storage system with integrated security providing
authentication and authorization services, customized storage interfaces could
be developed with exactly the overhead required for different applications. The
second phase of LWFS, known as Sirocco~\cite{sirocco}, is investigating how to
manage storage devices for efficient and scalable storage performance.  Sirocco
has been in process for three years and has a usable storage infrastructure
system.

%  This
%proposal seeks to build upon this work to demonstrate an application, data, and
%usage aware storage system optimized for exascale composite applications and
%capability application runs. We are proposing to combine the applications
%knowledge from ORNL with the SNL LWFS system and storage system knowledge, the
%metadata and storage systems knowledge of UCSC, and the middleware expertise of
%Rutgers to investigate how to make a data, workflow, and application aware
%storage system.

We will examine the research challenges from the perspective of the
%
(1) user of the system who is attempting to run an exascale simulation,
%
(2) the Storage System and I/O layer which needs to negotiate amongst all of
the users, and finally
%
(3) the user of the system who is attempting to understand the data which
was produced from their collection of simulations.

>>>>

To address these challenges we are proposing to combine knowledge
from a wide range of sources including ORNL applications, the ADIOS project,
the SNL Lightweight File Systems project and storage system knowledge, the metadata
management and storage systems knowledge of UCSC, and the middleware expertise
of Rutgers. We will integrate this diverse expertise to investigate how to make
a data, workflow, and application aware storage system.

@@

In this project we will extend ADIOS~\cite{adios} with new APIs and novel techniques
to coordinate with the storage back-end. The key idea is offering the ability to
negotiate with the storage system to agree on the tradeoff between data quality
and response time. We will test our ideas on the next generation OLCF,
SNL/LANL, and NERSC systems.
%
We plan to leverage the many inovations we discovered in 
the Lightweight File Systems~\cite{lwfs} (LWFS) project.
In this project, Sandia sought to
demonstrate stripping down a file system to the bare minimum features required
for any storage system. Then, additional functionality and semantics, such as
POSIX-style directories and consistency requirements, were added in using
auxiliary services separate from the stack or by layering providing a new
interface to the storage system. The project's first phase demonstrated that
using a core object storage system with integrated security providing
authentication and authorization services, customized storage interfaces could
be developed with exactly the overhead required for different applications. The
second phase of LWFS, known as Sirocco~\cite{sirocco}, is investigating how to
manage storage devices for efficient and scalable storage performance.  Sirocco
has been in process for three years and has developed a usable storage infrastructure.

We will examine the research challenges from the perspective of
%
(1) the user of the system who is attempting to run an exascale simulation,
%
(2) the Storage System and I/O layer which needs to negotiate between all of
the users, and finally
%
(3) the user of the system who is attempting to understand the data which
was produced from a set of simulations.
